\documentclass[a4paper,10pt]{article}
\usepackage[margin=0.5in,nofoot]{geometry}
\usepackage{fontawesome5}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{bookmark}


\hypersetup{
    colorlinks=true,
    linkcolor=black,
    filecolor=black,
    urlcolor=black,
    citecolor=black
}

\titleformat{\section}{\large\bfseries}{\thesection}{1em}{}[\titlerule]
\titlespacing*{\section}{0pt}{*1}{*1}

\newcommand{\entry}[4]{
  \noindent\textbf{#1} \hfill #2 \\
  \noindent\textit{#3} \hfill \textit{#4} \\
  \vspace{2pt}
}

\newcommand{\project}[2]{
  \noindent\textbf{#1} \hfill #2 \\
  \vspace{2pt}
}

\begin{document}

\pagenumbering{gobble}

\noindent
\begin{minipage}[t]{0.5\textwidth}
\textbf{\Large Armando A. von Grap Solheiro}

\vspace{0.4em}

\end{minipage}%
\begin{minipage}[t]{0.5\textwidth}
\raggedleft

São Paulo - Brazil

{\color{blue}} \href{tel:+5591980243595}{\faPhone \space (91) 98024-3595}
{\color{blue}} \href{mailto:avgsolheiro@gmail.com}{\faEnvelope \space avgsolheiro@gmail.com}

\vspace{0.2em}
 \quad
{\color{blue}} \href{https://github.com/asolheiro}{\faGithub \space GitHub} \quad
{\color{blue}} \href{https://www.linkedin.com/in/armandosolheiro/}{\faLinkedin \space LinkedIn} \\
\end{minipage}

\vspace{1em}

\begin{center}
    \textbf{\Large Site Reliability Engineer}
\end{center}
\vspace{0.5em}

\section*{Professional Summary}

IT professional focused on supporting platforms using DevOps and GitOps tools, such as Docker, Kubernetes, Helm, GitHub Actions and GitLabCI and on developing back-end applications and automations, with Go and Python.

Has a solid track record with web applications, RESTful APIs, automations, integrations and messaging systems, but also has specific experience with front-end, embedded systems and other programming languages.

\vspace{0.6em}

\vspace{0.5em}

\section*{Experience}

\vspace{0.6em}

\entry{JSRF Consulting}{\faCalendar \space January/2023 -- December/2024}{Freelance Developer}
\space
\vspace{-1.6em}
\begin{itemize}
\setlength\itemsep{0em}
\item Development of tools for event accreditation, reducing manual work and process time.
\item SaaS development to simplify manual work in law firms.
\item Development of chatbots to integrate customer services.
\end{itemize}

\entry{Banpará - Banco do estado do Pará}{\faCalendar \space August/2024 -- December/2024}{Systems Analyst}
\space
\vspace{-1.6em}
\begin{itemize}
\setlength\itemsep{0em}
\item Creation and standardization of legacy systems documentation required by the BACEN certification system.
\item Development of the internal supplier contract management system.
\item Standardization and updating of CI/CD systems tracks.
\end{itemize}

\entry{Jack Experts}{\faCalendar \space December/2024 -- Present}{DevOps Analyst}
\space
\vspace{-1.6em}
\begin{itemize}
\setlength\itemsep{0em}
\item Provisioning clusters with the company's standard stack: UI for management, monitoring and metrics collection, custom alerts, log centralization, scheduled backup, update and automation of routines.
\item Development of a tool to automate healthcheck routines and reports.
\item Migration of clusters between cloud providers, aiming for the lowest cost for the customer.
\item Creation of Cloud Native applications; thus providing packages compatible with all the most widely used tools on the market.
\item Development of tracks to automate the construction, provision and implementation of applications; thus minimizing manual work in the process and, therefore, human errors.
\end{itemize}

% \vspace{-1.6em}

\section*{Education}
\vspace{0.6em}

\entry{Estácio}{\faCalendar \space 2023 - 2026}{Technologist in Systems Analysis and Development}{\faMapMarker \space São Paulo - SP}

\entry{University of Amazônia}{\faCalendar \space 2020 - 2022}{Gastronomy}{\faMapMarker \space Belém - PA}


\section*{Technical skills}
\vspace{0.6em}
\begin{itemize}
\setlength\itemsep{0em}
\item Languages and Tools: Python, Go, FastAPI, Django.
\item Data bases: SQL, PostgreSQL, MySQL, Redis.
\item DevOps: Docker, Kubernetes, Helm, GitHub Action, GitLabCI
\item Others: Git, GitHub, GitLab, Linux, RabbitMQ, Markdown
\end{itemize}

\section*{Languages}
\vspace{0.6em}
\begin{itemize}
\setlength\itemsep{0em}
\item Portuguese: Native
\item English: Advanced.
\item French: Intermediate.
\item Spanish: Basic.
\end{itemize}

\end{document}